\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2014-12-03 paper/subdocuments/results.Rnw
vertippt: fixed

#Gini Range
gini_allcases <- gini(ns2010$income[ns1993_94$group=="pooled"]); gini_allcases
gini_normal <- gini(ns2010$income[ns1993_94$group=="normal"]); gini_normal
round(gini_allcases-gini_normal,3)
# 0.025

>>>>

#Gini Range
gini_allcases <- gini(ns2010$income[ns2010$group=="pooled"]); gini_allcases
gini_normal <- gini(ns2010$income[ns2010$group=="normal"]); gini_normal
round(gini_allcases-gini_normal,3)
# 0.02
